\documentclass{article}
\usepackage[margin=0.5cm]{geometry}
\usepackage{array}
\usepackage{longtable}
\usepackage{hyperref}


\begin{document}
    \begin{flushleft}
        \noindent
        \textbf{Name}: Dhruba Saha \\
        \textbf{Roll no.}: B.Sc(Sem-VI)Comp-04 \\
        \textbf{Department}: Department of Computer \& System Sciences, Siksha Bhavana \\
        \textbf{University}: Visva Bharati\\
        \textbf{Github Repository}: \url{https://github.com/dhrubasaha08/CC-14-Computer-Graphics-Lab}
    \end{flushleft}
    \begin{longtable}{|c|p{6cm}|c|}
        \hline
        \textbf{Sl. No.} & \textbf{Problem} & \textbf{Date of Submission} \\ \hline
        1 & Write a program in C to draw a line by using DDA algorithm when two points are given. [Use OpenGL Library] & 28/4/2023 \\ \hline
        2 & Write a program in C to draw a line by using Bresenham’s line drawing algorithm when two points are given. [Use OpenGL Library] & 28/4/2023 \\ \hline
        3 & Write a program in C to draw a circle by using midpoint circle drawing algorithm. [Use OpenGL Library] & 28/4/2023 \\ \hline
        4 & Write a program in C to draw an ellipse by using midpoint ellipse drawing algorithm. [Use OpenGL Library] & 28/4/2023 \\ \hline
        5 & Write a program in C to implement two-dimensional translation. Output depends upon user’s choice. [Use OpenGL Library] & 28/4/2023 \\ \hline
        6 & Write a program in C to implement two-dimensional rotation with respect to a pivot point. Output depends upon user’s choice. [Use OpenGL Library] & 29/4/2023 \\ \hline
         7 & Write a program in C to implement two-dimensional scaling with respect to a pivot point. Output depends upon user’s choice. [Use OpenGL Library] & 29/4/2023 \\ \hline
        8 & Write a program in C to implement two-dimensional reflection with respect to a pivot point. Output depends upon user’s choice. [Use OpenGL Library] & 29/4/2023 \\ \hline
        9 & Write a program in C to implement x-direction shear of an object in two-dimension relative to a line which is parallel to x-axis. Output depends upon user’s choice. [Use OpenGL Library] & 29/4/2023 \\ \hline
        10 & Write a program in C to implement point visibility algorithm. & 29/4/2023 \\ \hline
        11 & Write a program in C to implement end point code generation algorithm. & 29/4/2023 \\ \hline
        12 & Write a program in C to implement Cohen-Sutherland algorithm. & 29/4/2023 \\ \hline
        13 & Write a program in C to implement midpoint subdivision algorithm. & 28/4/2023 \\ \hline
        14 & Write a program in C to implement Cyrus-Beck algorithm. & 29/4/2023 \\ \hline
    \end{longtable}
\end{document}
